Digital economy in the UK: a multi-scalar story of the diffusion of web technologies

### 2023-03-22 paper/help/old/test.qmd

---
title: Title of submission to PLOS journal
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    corresponding: e.tranos@bristol.ac.uk
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
abstract: |
  blah blah

author_summary: |
  blah blah
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
header-includes:
- \usepackage{rotating, graphicx, dcolumn, booktabs, caption, xcolor}
editor_options: 
  markdown: 
    wrap: 72
---

```{r echo=FALSE, message = FALSE, warning=FALSE}
library(stargazer)
library(tidyverse)
#library(rmarkdown)
```

@@

<!-- motivation -->
@meade2021modelling There are numerous agents who would benefit from
accurate predictions of introduction times. These include: suppliers of
network equipment for production planning; suppliers of mobile phones
who need to have inventories of appropriately configured handsets;
international network planners who need to provide sufficient bandwidth
for communications between different countries; network operators and
regulatory authorities.

>>>>

---
title: "Digital economy in the UK; a multi-scalar story of the diffusion of web technologies"
format: 
  elsevier-pdf:
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      layout: onecolumn
      cite-style: number
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    corresponding: e.tranos@bristol.ac.uk
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
---

@@

<!-- motivation -->

### 2023-03-22 paper/help/old/tranos2023.Rmd

---
title: Digital economy in the UK: a multi-scalar story of the diffusion of web technologies
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    correspondingauthor: true
    footnote: 1
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  This paper maps the participation in the digital economy and its evolution in the UK over space and time. Most of the existing economic geography literature which dealt with the spatiality of the internet employed supply-side measures, such as infrastructural capacity, in order to understand the geography of the digital economy and its potential spatial economic effects. Useful as these approaches might have been, they cannot capture the micro-processes and the characteristics of the individual online behaviour. Using large volumes of archived and geolocated web content, this paper models the diffusion of web technologies over space and time in the UK. The data and geolocation strategy allow to capture these processes at a very granular spatial scale. The modelling approach, which is based on simple spatial analytical methods and on the estimation of diffusion curves at various scales, enables to depict the role of geography and other cognitive factors which drove the diffusion of web technologies. Although the focus is on a recent historical period -- 1996-2012 -- the results of the analysis depict diffusion mechanisms which can be very useful in understanding the evolutionary patterns of the adoption of other newer technologies.

keywords: 
  - keyword1
  - keyword2
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---
# Introduction {#sec:1}

>>>>

---
title: Digital economy in the UK; a multi-scalar story of the diffusion of web technologies
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    correspondingauthor: true
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
abstract: |
  This paper maps the participation in the digital economy and its evolution in the UK over space and time. Most of the existing economic geography literature which dealt with the spatiality of the internet employed supply-side measures, such as infrastructural capacity, in order to understand the geography of the digital economy and its potential spatial economic effects. Useful as these approaches might have been, they cannot capture the micro-processes and the characteristics of the individual online behaviour. Using large volumes of archived and geolocated web content, this paper models the diffusion of web technologies over space and time in the UK. The data and geolocation strategy allow to capture these processes at a very granular spatial scale. The modelling approach, which is based on simple spatial analytical methods and on the estimation of diffusion curves at various scales, enables to depict the role of geography and other cognitive factors which drove the diffusion of web technologies. Although the focus is on a recent historical period -- 1996-2012 -- the results of the analysis depict diffusion mechanisms which can be very useful in understanding the evolutionary patterns of the adoption of other newer technologies.
keywords: 
  - keyword1
  - keyword2
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---
# Introduction {#sec:1}

### 2023-03-22 paper/help/old/tranos2023.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Digital economy in the UK: a multi-scalar story of the diffusion of web technologies},
  pdfauthor={Emmanouil Tranos},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Digital economy in the UK: a multi-scalar story of the diffusion
of web technologies}
\author[1]{Emmanouil Tranos%
\corref{cor1}%
}
 \ead{e.tranos@bristol.ac.uk}

\affiliation[1]{organization={University of Bristol and The Alan Turing
Institute},postcode={UK},postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
This paper maps the participation in the digital economy and its
evolution in the UK over space and time. Most of the existing economic
geography literature which dealt with the spatiality of the internet
employed supply-side measures, such as infrastructural capacity, in
order to understand the geography of the digital economy and its
potential spatial economic effects. Useful as these approaches might
have been, they cannot capture the micro-processes and the
characteristics of the individual online behaviour. Using large volumes
of archived and geolocated web content, this paper models the diffusion
of web technologies over space and time in the UK. The data and
geolocation strategy allow to capture these processes at a very granular
spatial scale. The modelling approach, which is based on simple spatial
analytical methods and on the estimation of diffusion curves at various
scales, enables to depict the role of geography and other cognitive
factors which drove the diffusion of web technologies. Although the
focus is on a recent historical period -- 1996-2012 -- the results of
the analysis depict diffusion mechanisms which can be very useful in
understanding the evolutionary patterns of the adoption of other newer
technologies.
\end{abstract}

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

\renewcommand\refname{References}
  \bibliography{bibliography}

>>>>

\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

  \journal{An awesome journal} % Sets Journal name

\usepackage{lineno} % add

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Digital economy in the UK; a multi-scalar story of the diffusion of web technologies},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\begin{frontmatter}

  \title{Digital economy in the UK; a multi-scalar story of the
diffusion of web technologies}
    \author[University of Bristol and The Alan Turing
Institute]{Emmanouil Tranos%
  \corref{cor1}%
  }
   \ead{e.tranos@bristol.ac.uk} 
      \affiliation[University of Bristol and The Alan Turing
Institute]{University of Bristol, School of Geographical Sciences,
Bristol, UK; The Alan Turing Institute, London, UK}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  This paper maps the participation in the digital economy and its
  evolution in the UK over space and time. Most of the existing economic
  geography literature which dealt with the spatiality of the internet
  employed supply-side measures, such as infrastructural capacity, in
  order to understand the geography of the digital economy and its
  potential spatial economic effects. Useful as these approaches might
  have been, they cannot capture the micro-processes and the
  characteristics of the individual online behaviour. Using large
  volumes of archived and geolocated web content, this paper models the
  diffusion of web technologies over space and time in the UK. The data
  and geolocation strategy allow to capture these processes at a very
  granular spatial scale. The modelling approach, which is based on
  simple spatial analytical methods and on the estimation of diffusion
  curves at various scales, enables to depict the role of geography and
  other cognitive factors which drove the diffusion of web technologies.
  Although the focus is on a recent historical period -- 1996-2012 --
  the results of the analysis depict diffusion mechanisms which can be
  very useful in understanding the evolutionary patterns of the adoption
  of other newer technologies.
  \end{abstract}
    \begin{keyword}
    keyword1 \sep 
    keyword2
  \end{keyword}

 \end{frontmatter}

@@

\renewcommand\refname{References}
\bibliography{mybibfile.bib}

### 2023-03-22 paper/submission1/help.Rmd

@@

Space: absorptive capacity

Evolutionary economic geography >> path dependency

>>>>

grubler1990rise The scale of spatial innovation diffusion is similar to
that of temporal diffusion models: hierarchically decomposed.

@@

<!-- Space: absorptive capacity -->

<!-- Evolutionary economic geography >> path dependency -->

@bento2015spatial The concept of absorptive capacity has also been
applied in the TIS context in terms of the con-struction of capacity
needed to transfer and implement a new technology in the receiving
country (cf.Van Alphen, 2011), with repercussions for the nature of
system functions

@bednarz2020pulled larger local technological niches (at least from a
demand perspective) are more likely to be formed in urban areas than in
rural ones, which is in line with the work of Ha¨gerstrand (1965a,b).
However, size is not the only regional characteristic that may matter in
this context. Regions also differ in accumulated experiences and the
presence of tacit knowledge with respect to products, as well as in
actors' propensity share this knowledge among producers (Martin et al.,
2019)

### 2023-03-22 paper/submission1/tranos2023.qmd

# Introduction {#sec:1}

Geographers were always interested in how new technologies and
innovations diffuse across space and, importantly, how such
spatio-temporal processes can be modelled. The seminal contribution of
@hagerstrand1968innovation is illustrative of this early interest.
However, the torch of exploring and modelling such processes had been
passed to other disciplines such as economics, business studies and
sociology well before the 'cultural turn' of economic geography
[@perkins2005international]. A potential explanation of lack of studies
exploring the diffusion of new and, more specifically, digital
technologies across *both* space and time can be attributed to the
scarcity of relevant and granular enough data. As @zook2022mapping
highlight, digital activities are hardly ever captured in official data.

This paper aims to reinstate geographers' interest in how new and
digital technologies diffuse over space and time. It adopts a geographic
standpoint to explore and map the diffusion of web technologies in the
UK over space and time. It does so by employing a novel source of big
data which captures the active engagement with web technologies during
the $1996-2013$ period.

The motivation for this paper lies in the fact that there are various
stakeholders who are interested in knowing how new digital technologies
diffused over space and time use this information to make predictions
regarding the diffusion of related future technologies. As per
@meade2021modelling a variety of actors have a direct interest in
gaining such knowledge including network equipment suppliers; network
operators, regulatory and local authorities. And despite the spatial
heterogeneity of such diffusion mechanisms and the policy relevance,
there are very limited attempts in the literature to analyse the
diffusion of new digital technologies at a granular level.

the paper answers an empirical question: how did a

@zook2022mapping Because new digital activities are rarely---if
ever---captured in official state data, researchers must rely on
information gathered from alternative sources. With this in mind, the
overarching aim of this article is outlining an approach for analyzing
the "new spaces and geographies" of digital phenomena and practices.

<!-- motivation -->

Classifying adopters of a technology along a time axis was pioneered by
Rogers (1962), who categorized adopters into five groups as innovators,
early adopters, early majority, late majority and laggards.

An a priori approach groups similar countries into segments, where
similarity is defined using economic, social, or political covariates.
Examples include Hofstede (2001) and Lee (1990). An a posteriori
analysis considers segments based on realized market behaviour, for
example see Sood et al. (2009). Some studies investigate changing
segment membership over time, see Cannon and Yaprak (2011).

@fritsch2015new Hägerstrand (1952, 1967) was the first scholar to
intensively analyze spatial diffusion pro cesses. Based on the empirical
observations of the regional spread of process innovations, he
hypothesized that new technology is first implemented in the 'center' --
the large agglom erations -- and then moves 'down' the spatial
hierarchy, the last stop being the 'periphery', i.e. remote and sparsely
populated regions. There are at least two factors that may explain this
pattern: first, the transfer of tacit knowledge via face-to-face contact
and second, the absorptive capacity of a region.

<!-- key concepts -->

@bento2015spatial The concept of absorptive capacity has also been
applied in the TIS context in terms of the con-struction of capacity
needed to transfer and implement a new technology in the receiving
country (cf.Van Alphen, 2011), with repercussions for the nature of
system functions

@bednarz2020pulled larger local technological niches (at least from a
demand perspective) are more likely to be formed in urban areas than in
rural ones, which is in line with the work of Ha¨gerstrand (1965a,b).
However, size is not the only regional characteristic that may matter in
this context. Regions also differ in accumulated experiences and the
presence of tacit knowledge with respect to products, as well as in
actors' propensity share this knowledge among producers (Martin et al.,
2019)

<!-- @das2022diffusion -->

<!-- Epidemic approach: The approach emphasizes that the adoption of a -->

<!-- technology spreads like an infection among the potential adopters. By -->

<!-- taking a homogeneous group of potential adopters as an assumption, it -->

<!-- explains the adoption of any innovation. -->

To summarize the discussion, first, here the diffusion process is
selfperpetuating as initial use stimulates further use. Second, it
follows a disequilibrium path as the level of users is always lower than
the number of potential users (Stoneman 2002).

The criticisms are mainly based on the fact that although the approach
gives an idea of aggregate (industry or household) behaviour, it does
not focus on the individual's (firm or household) adoption process

<!-- Rogers3, that divides adopters as: (I.) Innovators: first 2.5%, (II.) -->

<!-- Early adopters: next 13.5%, (III.) Early Majority: following 34%, (IV.) -->

<!-- Late Majority: next 34%, and the rest as (V.) Laggards -->

@morrill2020spatial Spatial diffusion is the process by which behavior
or characteristics of the landscape change as a result of what happens
elsewhere earlier. Spatial diffusion is the spread of the phenomenon,
over space and timed, from limited origins

Contagious diffusion=\> spatial autocorelation

expansion-type diffusion

<!-- the three geographic diffusion processes are (1) purely contagious where -->

<!-- distance or adjacency is the absolute controlling factor, (2) purely -->

<!-- hierarchical where size or urban position in the central place hierarchy -->

<!-- is the absolute controlling factor, or (3) where the location of change -->

<!-- is purely random. These are the pure or ideal forms of the diffusion -->

<!-- process; all real diffusion processes are the result of a combination of -->

<!-- these extremes. -->

The work by the communication sociologist Everett Rogers (1962, 1971,
1983) has emphasized the role of information, communication, formal and
informal media, opinion leaders and social networks, and economic and
psychological constraints on acceptance. Rogers's work stresses the
decision mechanism of the potential adopter; the work of Rogers
partitions the adopter's process of choosing to accept a new phenomenon
or trait into five stages: stage 1--the potential adopter gains
knowledge or awareness of an innovation; stage 2--persuasion is
exercised to adopt; stage 3--a decision is made to adopt; stage 4--the
decision to adopt is implemented; stage 5--the adopter confirms the
decision to adopt. In Rogers's stage theory there may be a substantial
time lag between when a potential adopter becomes aware of the new
characteristic and when a decision is actually made to adopt.

Hägerstrand considered diffusion to be a fundamental geographic process:
Whatever the phenomenon being diffused might be, one may consider it in
the context of a larger universal process of spatial diffusion.

<!-- @das2022diffusion [not good paper] Invention, innovation and diffusion -->

<!-- are considered as the three pillars of the theory of technological -->

<!-- change and Schumpeter is considered as the father of the study of -->

<!-- diffusion -->

@leibowicz2016representing Diffusion is a spatial (Hagerstrand, 1967) as
well as a temporal process, and historical evidence confirms that
technologies diffuse at different times, at different rates, and to
different extents in different places, and can be significantly
influenced by policies (Victor, 1993).

<!-- @leibowicz2016representing -->

<!-- An illustrative empirically based theory for technology -->

<!-- diffusion across multiple regions is suggested by "Schmidt's Law" -->

<!-- (Grubler, 1990). With respect to a specific technology, it divides -->

<!-- regions into three groups: core, rim, and periphery. The core is where -->

<!-- the technology is invented, subject to experimentation, and first -->

<!-- deployed commercially. To develop the technology, the core must have -->

<!-- both sufficient innovative ability and economic motivation to make the -->

<!-- necessary resource commitment. As the technology spreads from the core -->

<!-- to the rim and eventually to the periphery, later adopters have the -->

<!-- advantage of benefiting from the experiences of earlier adopters via -->

<!-- knowledge spillover effects (Verdolini and Galeotti, 2011). At this -->

<!-- point, the technology has likely been refined and costs have likely -->

<!-- declined significantly. Schmidt's Law claims that, as a result, -->

<!-- diffusion proceeds at a faster rate in regions which adopt the -->

<!-- technology later. However, diffusion tends to be less pervasive in -->

<!-- regions where adoption is delayed, ultimately saturating at a lower -->

<!-- extent than in regions where adoption occurred earlier. This is often -->

<!-- attributed to a lack of proper institutions and infrastructures in later -->

<!-- adopters, markets whichmay not be as favorable to a technology, or the -->

<!-- availability of yet newer options that invite technological -->

<!-- leapfrogging. -->

Lastly, it can be globally optimal for innovative economies to deploy
advanced technologies more than what is locally optimal if this enables
faster diffusion in less advanced regions that could benefit from the
technology.

@@

<!-- @grubler1990rise Following the definition given by Rogers, 1983, -->

<!-- diffusion is the process by which an innovation is communicated through -->

<!-- certain communication channels over time among the members of a social -->

<!-- system. An innovation may be an idea, object or practice which is -->

<!-- perceived as new by an individual or another unit of adoption (e.g., an -->

<!-- organization) . Communication via communication channels refers to how -->

<!-- knowledge about an innovation is transferred between the members of a -->

<!-- social system. Communication takes time, and is therefore an important -->

<!-- aspect of innovation diffusion. In fact, all theoretical and empirical -->

<!-- diffusion studies agree that an innovation does not instantly diffuse -->

<!-- into a social system. Instead a typical time pattern of diffusion along -->

<!-- a S-shaped trajectory seems to be the rule. The S-shaped pattern of -->

<!-- diffusion appears to be a basic anthropologic phenomenon, as it is also -->

<!-- confirmed by a large number of studies· of primitive preindustrial -->

<!-- societies. -->

grubler1990rise The scale of spatial innovation diffusion is similar to
that of temporal diffusion models: hierarchically decomposed.

<!-- grubler1990rise -->

<!-- Spatial innovation diffusion in Hagerstrand's model consists of three -->

<!-- stages. Stage 1: Local concentrations of initial acceptances (initial -->

<!-- agglomeration) . Stage 2: Radial dissemination outward from the initial -->

<!-- agglomeration, accompanied by the rise of secondary agglomerations. -->

<!-- Stage 3: The condensing and saturation stage, in which filling-in occurs -->

<!-- and diffusion eventually ceases. -->

<!-- grubler1990rise -->

<!-- Thus, three main characteristics define the spatial diffusion process: -->

<!-- (1) As in temporal diffusion models, an S-shaped pattern in the -->

<!-- cumulative level of adoption. (2) A "hierarchy effect" by which -->

<!-- diffusion proceeds from initial centers to secondary ones. Within the -->

<!-- context of urban systems (central places) this implies a hierarchical -->

<!-- spread of an innovation from larger to smaller centers, and from the -->

<!-- centers to the surrounding hinterland. (3) A "neighborhood effect" Le., -->

<!-- diffusion proceeds outwards from innovation centers, first "hitting" -->

<!-- (Brown, 1981) nearby rather than far-away locations. -->

@@

Either way, the strong assumption is that developing countries can
acquire modern technology innovated in developed economies, often at a
fraction of the original research and development (R&D) costs, thereby
leapfrogging many decades of technological progress (Teece 2000).

The first involves a country's geographical location. Recent empirical
work suggests that diffusion is ''geographically localized'' (Globerman,
Kokko, and Sjo¨holm 2000; Keller 2002; Milner 2003) in that a technology
diffuses faster in a country where it is already more widely diffused in
neighboring countries. Underlying these regional effects are contagion
and contact with prior users or producers of technology.

@ding2010modeling Rogers (1995) characterized early adopters as
knowledgeable risk takers. Griliches (1957) looked at the rate of return
for early adopters and characterized them as profit maximizers. The
geographer Hagerstrand (1967) was focusing on the character of early
adopters in the transmittal process that produces follow-on participants
in the process. Space was treated as a contiguity system with embedded
characteristics producing barrier elements to the diffusion process.

@ding2010modeling REVIEW ON Technological Diffusion

<!-- Hagerstrand (1968) was the first to demonstrate that diffusion typically -->

<!-- starts from innovative centers ('core´) and disseminates, through a -->

<!-- hierarchy of subcenters, to the periphery. This process is sequential -->

<!-- rather than simultaneous, and tends to accelerate from core to -->

<!-- periphery, where diffusion reaches a lower intensity than in the core -->

<!-- (Hagerstrand, 1968; Grubler, 1990; Morrill, 2005). A similar effect of -->

<!-- spatial acceleration has been identified in marketing research and is -->

<!-- known as the "lead-lag effect" (Peres et al., 2010). -->

@perkins2011internet Two main mechanisms are identified in the
literature to explain diffusion: (1) epidemic-type dynamics whereby
contact with previous adopters stimulates uptake as po tential adopters
learn about a new innovation; and (2) economic-type mechanisms whereby
potential users adopt a new innovation as it be comesmore profitable,
useful, or valuable, with uptake characteristically spreading as costs
be come lower, performance improves, or the po tential uses of the
innovation grow over time.

To this extent, our results contribute to a growing body of work that
has sought to caution against claims about the supposed novelty of the
Internet and the suggestion that it is somehow different.

@@

# Literature review {#sec2} MAYBE SKIP THIS??

@@

>>>>

# Introduction {#sec1}

Geographers were always interested in how new technologies and
innovations diffuse across space and, importantly, how such
spatio-temporal processes can be modelled. After all, diffusion together 
with invention and innovation are considered the pillars of 
technological change [@das2022diffusion]. The seminal contribution of
@hagerstrand1968innovation is illustrative of this early interest.
However, the torch of exploring and modelling such processes had been
passed to other disciplines such as economics, business studies and
sociology well before the 'cultural turn' of economic geography
[@perkins2005international]. A potential explanation of the lack of 
geographical studies exploring the diffusion of new and, more 
specifically, digital technologies across *both* space and time can be
attributed to the scarcity of relevant and granular enough data. As 
@zook2022mapping highlight, digital activities are hardly ever captured 
in official data.

This paper offers such a contribution: a geographical study illustrating 
how a new technology that is the web diffused over space and time 
in the UK at a high level of spatial granularity during the $1996-2012$ 
period. It does so by employing a novel source of big data which 
captures the active engagement with web technologies during that period.
By addressing this empirical question this paper exemplifies how the 
combination of data sources which escape the traditional social science
domain and adequate research methods can offer new contributions 
regarding our understanding of technologies are diffused.

The motivation for this paper lies in the fact that there are various
stakeholders who are interested in knowing how new digital technologies
diffused over space and time and use this information to make predictions
regarding the diffusion of related *future* technologies.
As per @leibowicz2016representing, historical studies agree on the fact that 
"technologies diffuse at different times, at different rates, and to
different extents in different places, and can be significantly
influenced by policies [@victor1993]". @meade2021modelling highlight that 
a variety of actors have a direct interest in gaining such knowledge 
including network equipment suppliers; network operators, regulatory 
and local authorities. 
These processes and their effects very a lot between scales: although
the diffusion of a new technology might not be optimal at a local level,
it might be beneficial from a global perspective as it might enable 
faster diffusion to less advantaged places @leibowicz2016representing. 
Despite the spatial heterogeneity of such diffusion mechanisms and 
the policy relevance, there are very limited attempts in the literature 
to analyse the diffusion of new digital technologies at a detailed 
geographical level.

<!-- diffusion and adoption -->

Technological diffusion, which is by definition an aggregated process, 
can be discussed in parallel with individual adoption mechanisms.
On the one hand, @rogers2010diffusion identifies early adopter of new 
technologies as 'knowledgeable risk takers' and @griliches1957 as 'profit 
maximisers' [@ding2010modeling]. Such individual agents are rewarded because 
of their attitude towards new technologies and innovations. On the other hand,
@perkins2011internet attribute diffusion to two processes: (i) epidemic-type 
of mechanisms, which

Two main mechanisms are identified in the
literature to explain diffusion: (1) epidemic-type dynamics whereby
contact with previous adopters stimulates uptake as po tential adopters
learn about a new innovation; and (2) economic-type mechanisms whereby
potential users adopt a new innovation as it be comesmore profitable,
useful, or valuable, with uptake characteristically spreading as costs
be come lower, performance improves, or the po tential uses of the
innovation grow over time.
The criticisms are mainly based on the fact that although the approach
gives an idea of aggregate (industry or household) behaviour, it does
not focus on the individual's (firm or household) adoption process

@morrill2020spatial understands spatial diffusion as the landscape 
changes that spread across space because of changes that take place 
elsewhere.

<!-- data and early engagement with the web -->

@@

@@

@@

# Literature review {#sec2}

MAYBE SKIP THIS??

@@

@perkins2005internationalEither way, the strong assumption is that developing countries can
acquire modern technology innovated in developed economies, often at a
fraction of the original research and development (R&D) costs, thereby
leapfrogging many decades of technological progress (Teece 2000).

@perkins2005international The first involves a country's geographical location. Recent empirical
work suggests that diffusion is ''geographically localized'' (Globerman,
Kokko, and Sjo¨holm 2000; Keller 2002; Milner 2003) in that a technology
diffuses faster in a country where it is already more widely diffused in
neighboring countries. Underlying these regional effects are contagion
and contact with prior users or producers of technology.
